The \vspec{} Collection: A suite of utilities to model spectroscopic phase curves of 3D exoplanet atmospheres in the presence of stellar variability.

### 2024-08-02 src/tex/ms.tex
Fix weird bug with url

% Define document class
\documentclass[twocolumn,linenumbers]{aastex631}
\usepackage{showyourwork}
\usepackage[version=4]{mhchem}
\usepackage{listings}

@@

\newcommand{\urldocsvspec}{\url{https://vspec-collab.github.io/VSPEC/0.6.0/index.html}}
\newcommand{\urldocsvspecvsm}{\url{https://vspec-vsm.readthedocs.io/en/latest/}}
\newcommand{\urldocspypsg}{\url{https://tedjohnson12.github.io/pypsg/}}
\newcommand{\urldocsgridpolator}{\url{https://vspec-collab.github.io/GridPolator/}}

@@

The flow of \vspec{}'s code is broken into three parts: i) read in the configuration, ii) compute planetary spectra, and iii) compute stellar spectra. Detailed API documentation, configuration parameter descriptions, and examples can be found on the \vspec{} documentation page\footnote{\urldocsvspec}.
\subsection{Configuring \vspec{}}
\label{subsec:config}

\vspec{} configurations are designed to minimize human errors by providing two equivalent formats. The first, a file written in YAML, is optimized for
human readability. For example, the \texttt{system} section, which describes the relationship between the observed planetary system and the observer, could
be written:
\begin{lstlisting}[label={ls:yaml},caption={\vspec{} YAML Configuration}]
system:
    distance: 12.4 pc
    inclination: 89.7 deg
    phase_of_periastron: 0 deg
\end{lstlisting}
Note that the units of each of these parameters is included in a human-readable way. Internally, \vspec{} casts each of these parameters to an Astropy
\texttt{Quantity} instance, so that the user can input any desired value and unit combination so long as the physical type is correct -- i.e. it would be
equivalent to write \texttt{3.83e17 m} as the value for the \texttt{distance} parameter.

>>>>

% Define document class
\documentclass[twocolumn,linenumbers]{aastex631}
\usepackage{showyourwork}
\usepackage[version=4]{mhchem}
\usepackage{listings}
\usepackage{hyperref}

@@

\newcommand{\urldocsvspecvsm}{\url{https://vspec-vsm.readthedocs.io/en/latest/}}
\newcommand{\urldocspypsg}{\url{https://tedjohnson12.github.io/pypsg/}}
\newcommand{\urldocsgridpolator}{\url{https://vspec-collab.github.io/GridPolator/}}

@@

The flow of \vspec{}'s code is broken into three parts: i) read in the configuration, ii) compute planetary spectra, and iii) compute stellar spectra.
See the \vspec{} documentation page\footnote{\href{https://vspec-collab.github.io/VSPEC/0.6.0/index.html}{https://vspec-collab.github.io/VSPEC/0.6.0/index.html}} for detailed API documentation.
\subsection{Configuring \vspec{}}
\label{subsec:config}

\vspec{} configurations are designed to minimize human errors by providing two equivalent formats. The first, a file written in YAML, is optimized for
human readability. For example, the \texttt{system} section, which describes the relationship between the observed planetary system and the observer, could
be written:
\begin{lstlisting}[
    label={ls:yaml},
    caption={\vspec{} YAML Configuration}
]
system:
    distance: 12.4 pc
    inclination: 89.7 deg
    phase_of_periastron: 0 deg
\end{lstlisting}
Note that the units of each of these parameters is included in a human-readable way. Internally, \vspec{} casts each of these parameters to an Astropy
\texttt{Quantity} instance, so that the user can input any desired value and unit combination so long as the physical type is correct -- i.e. it would be
equivalent to write \texttt{3.83e17 m} as the value for the \texttt{distance} parameter.
